---
title: "Auxiliary data to Automatic Responses to Acoustically Rough Intervals"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output: html_document
bibliography: refs.bib
biblio-style: "apalike"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
_Created: 26/12/2021_.

These files contains the data and analysis scripts for "Automatic Responses to Acoustically Rough Intervals" concerning computational models of roughness and harmonicity.

## Harmonicity

Harmonicity for three common models: @harrison2018, @parncutt1988 and @milne2013computational, including the ranks of the model means and the model correlations.

```{r,echo=TRUE,results='asis',warning=FALSE,message=FALSE}
# Harmonicity 3 models: Harrison and Pearce 2018, Parncutt88, Milne13 
source('model_harmonicity_data.R')
```

## Roughness

Roughness values for three common models: @hutchknopoff1978, @vassilakis2001perceptual, and @wang2013roughness, including the ranks of the model means and the model correlations.

```{r,echo=TRUE,results='asis',warning=FALSE,message=FALSE}
# Roughness 3 models: Hutchinson, Vassilakis, Wang
source('model_roughness_data.R')
```

## Empirical dissonance ratings

Empirical ratings from classic studies by @Huron1994 and @bowling2018.

```{r,echo=TRUE,results='asis',warning=FALSE,message=FALSE}
# Empirical data from Huron 94 and Bowling
source('empirical_data.R')
```

## Create variable deltas for the interval pairs

```{r,echo=TRUE,results='asis',warning=FALSE,message=FALSE}
source('deltas.R')
```

# Create graphs for selected stimuli

Take four intervals that together span low to high delta in roughness and plot the amplitude and spectra for each.

```{r,echo=FALSE,warning=FALSE,message=FALSE,fig.width=8}
source('figure_stimuli.R') # Completed in 1 December 2020
```

# References

<div id="refs"></div>

