---
title: "Computational models related to Automatic Responses to Acoustically Rough Intervals"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
bibliography: refs.bib
biblio-style: "apalike"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Release Notes

_Created: 1/2/2021_.

These files contains the computational models for "Automatic Responses to Acoustically Rough Intervals", particularly the models of roughness and harmonicity. See also the behavioural data and the analyses at a [separate repository](https://tuomaseerola.github.io/primingroughnessdata/). The data is also available at OSF: [https://osf.io/zmjpd/](https://osf.io/zmjpd/).

The paper is:
>Armitage, J., Lahdelma, I., & Eerola, T. (2021). Automatic responses to musical intervals: Contrasts in acoustic roughness predict affective priming in Western listeners. _Journal of Acoustical Society of America, 150(551)_. https://doi.org/10.1121/10.0005623


# Harmonicity

Harmonicity for three common models: @harrison2018, @parncutt1988 and @milne2013computational, including the ranks of the model means and the model correlations.

```{r,echo=TRUE,results='asis',warning=FALSE,message=FALSE}
# Harmonicity 3 models: Harrison & Pearce 2018, Parncutt 1988, Milne 2013 
source('model_harmonicity_data.R')
```

# Roughness

Roughness values for three common models: @hutchknopoff1978, @vassilakis2001perceptual, and @wang2013roughness, including the ranks of the model means and the model correlations.

```{r,echo=TRUE,results='asis',warning=FALSE,message=FALSE}
# Roughness 3 models: Hutchinson 1978, Vassilakis 2001, Wang et al 2013
source('model_roughness_data.R')
```

# Empirical dissonance ratings

Empirical ratings from classic studies by @Huron1994 and @bowling2018.

```{r,echo=TRUE,results='asis',warning=FALSE,message=FALSE}
# Empirical data from Huron 1994 and Bowling et al 2018
source('empirical_data.R')
```

# Create variable deltas for the interval pairs

```{r,echo=TRUE,results='asis',warning=FALSE,message=FALSE}
source('deltas.R')
```

# Create graphs for selected stimuli

Take four intervals that together span low to high delta in roughness and plot the amplitude and spectra for each.

```{r,echo=FALSE,warning=FALSE,message=FALSE,fig.width=8}
source('figure_stimuli.R') # Completed in 1 December 2020
```

# References

<div id="refs"></div>

